---
title: "ALL PROBATILITIES AT ONE TOGETHER"
#author: "CHENRUJIE"
#date: "2022年8月28日"
output: 
  html_document: 
    toc: true
    toc_float: true
    theme: darkly
---

```{r setup, include=FALSE}
# Libraries.--------------------------------------------------------------------
library(readr)
library(timeDate)
library(timeSeries)
library(readr)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
allProba_filepath <- file.path("~/finalProba/allProba")
allProba_filelist <- list.files(allProba_filepath)

```

All probabilities are assemble here, from PRO80 project, sentiCourse project, sentiMacro project and others. And I am trying to use the ensemble approach to generate the final probability result which should be guiding my trade

# DIRECT LISTING.

```{r Loading Daily Trading Data, echo=FALSE, paged.print=FALSE}
## Loading All Trading Data pre processing.=====================================
pro80_filelist = grep('\\pro80', allProba_filelist, value = TRUE)
sentiCourse_filelist = grep('dicingerpro', allProba_filelist, value = TRUE)
allProba_filelist
```

## Probability from PRO80 Project {.tabset}

### CU0 Related

```{r}
filename = grep('cu0', pro80_filelist, value = TRUE)
pro80_cu0_related <- read_csv(file.path(allProba_filepath, filename))
pro80_cu0_related_df <- as.data.frame(pro80_cu0_related[-1])
rownames(pro80_cu0_related_df) <- pro80_cu0_related$...1
knitr::kable(pro80_cu0_related_df)
```

### RB0 Related

```{r}
filename = grep('rb0', pro80_filelist, value = TRUE)
pro80_rb0_related <- read_csv(file.path(allProba_filepath, filename))
pro80_rb0_related_df <- as.data.frame(pro80_rb0_related[-1])
rownames(pro80_rb0_related_df) <- pro80_rb0_related$...1
knitr::kable(pro80_rb0_related_df)
```

### SCM Related

```{r}
filename = grep('SCM', pro80_filelist, value = TRUE)
pro80_SCM_related <- read_csv(file.path(allProba_filepath, filename))
pro80_SCM_related_df <- as.data.frame(pro80_SCM_related[-1])
rownames(pro80_SCM_related_df) <- pro80_SCM_related$...1
knitr::kable(pro80_SCM_related)
```

## Probability from sentiCourse Project {.tabset}

### dicingerPro_TD

```{r}
filename = grep('dicingerpro_TD', sentiCourse_filelist, value = TRUE)
dicingerPro_TD <- read_csv(file.path(allProba_filepath, filename))
dicingerPro_TD.df <- as.data.frame(dicingerPro_TD[-1])
rownames(dicingerPro_TD.df) <- paste('dicingerPro_TD', c("linear", "CNN", "RNN"), sep=".")
knitr::kable(t(dicingerPro_TD.df))
```

### dicingerPro_S

```{r}
filename = grep('dicingerpro_S', sentiCourse_filelist, value = TRUE)
dicingerPro_S <- read_csv(file.path(allProba_filepath, filename))
dicingerPro_S.df <- as.data.frame(dicingerPro_S[-1])
rownames(dicingerPro_S.df) <- paste('dicingerPro_S', c("linear", "CNN", "RNN"), sep=".")
knitr::kable(t(dicingerPro_S.df))
```

The table preprocessing all the data should include the following features: 
up_flag, down_flag, acc.

```{r DESIGNING THE TABLE}
library(tidyverse)
# # Functions.------------------------------------------------------------------
# Function to create probability table of given target index
create_Proba <- function(indexWanted){
  Proba.df <- data.frame(matrix(nrow = 9, ncol = 5))
  colnames(Proba.df) <- c("target", "module", "up_flag", "down_flag", "acc.")
  Proba.df$module <- c("ABOVEorBELOW",
                       "UPorDOWN", 
                       "STRONGorWEAK",
                       "dicingerPro_TD.linear",
                       "dicingerPro_TD.CNN",
                       "dicingerPro_TD.RNN",
                       "dicingerPro_S.linear",
                       "dicingerPro_S.CNN",
                       "dicingerPro_S.RNN")
  rownames(Proba.df) <- Proba.df$module
  ind <- paste0(indexWanted, '_60')
  Proba.df$target <- ind
  pattern = paste0("^", indexWanted)

  # Read ABOVEorBELOW module, assume the accuracy to be slightly above half a point to be 0.55
  if(ind%in%colnames(pro80_cu0_related_df)){
    Proba.df["ABOVEorBELOW", "up_flag"] <- pro80_cu0_related_df["ABOVE_TREND", ind]
    Proba.df["ABOVEorBELOW", "down_flag"] <- pro80_cu0_related_df["BELOW_TREND", ind]
  }else if(ind%in%colnames(pro80_rb0_related_df)){
    Proba.df["ABOVEorBELOW", "up_flag"] <- pro80_rb0_related_df["ABOVE_TREND", ind]
    Proba.df["ABOVEorBELOW", "down_flag"] <- pro80_rb0_related_df["BELOW_TREND", ind]
  }else if(ind%in%colnames(pro80_SCM_related_df)){
    Proba.df["ABOVEorBELOW", "up_flag"] <- pro80_SCM_related_df["ABOVE_TREND", ind]
    Proba.df["ABOVEorBELOW", "down_flag"] <- pro80_SCM_related_df["BELOW_TREND", ind]
  }
  Proba.df["ABOVEorBELOW", "acc."] <- c(0.70)

  # Read UPorDOWN module, assume the accuracy to be slightly above half a point to be 0.55
  if(ind%in%colnames(pro80_cu0_related_df)){
    Proba.df["UPorDOWN", "up_flag"] <- pro80_cu0_related_df["TREND_UP", ind]
    Proba.df["UPorDOWN", "down_flag"] <- pro80_cu0_related_df["TREND_DOWN", ind]
  }else if(ind%in%colnames(pro80_rb0_related_df)){
    Proba.df["UPorDOWN", "up_flag"] <- pro80_rb0_related_df["TREND_UP", ind]
    Proba.df["UPorDOWN", "down_flag"] <- pro80_rb0_related_df["TREND_DOWN", ind]
  }else if(ind%in%colnames(pro80_SCM_related_df)){
    Proba.df["UPorDOWN", "up_flag"] <- pro80_SCM_related_df["TREND_UP", ind]
    Proba.df["UPorDOWN", "down_flag"] <- pro80_SCM_related_df["TREND_DOWN", ind]
  }
  Proba.df["UPorDOWN", "acc."] <- c(0.80)
  
  # Read STRONGorWEAK module, assume the accuracy to be slightly above half a point to be 0.55
  if(ind%in%colnames(pro80_cu0_related_df)){
    Proba.df["STRONGorWEAK", "up_flag"] <- pro80_cu0_related_df["STRONG", ind]
    Proba.df["STRONGorWEAK", "down_flag"] <- pro80_cu0_related_df["WEAK", ind]
  }else if(ind%in%colnames(pro80_rb0_related_df)){
    Proba.df["STRONGorWEAK", "up_flag"] <- pro80_rb0_related_df["STRONG", ind]
    Proba.df["STRONGorWEAK", "down_flag"] <- pro80_rb0_related_df["WEAK", ind]
  }else if(ind%in%colnames(pro80_SCM_related_df)){
    Proba.df["STRONGorWEAK", "up_flag"] <- pro80_SCM_related_df["STRONG", ind]
    Proba.df["STRONGorWEAK", "down_flag"] <- pro80_SCM_related_df["WEAK", ind]
  }
  Proba.df["STRONGorWEAK", "acc."] <- c(0.90)
  
  dfind <- grep(pattern, colnames(dicingerPro_TD.df))
  # Read dicingerPro_TD.linear module
  if(length(dfind)==2){
    if(dicingerPro_TD.df['dicingerPro_TD.linear', dfind[2]] == 0){
      Proba.df['dicingerPro_TD.linear', "up_flag"] <- 0
      Proba.df['dicingerPro_TD.linear', "down_flag"] <- 1
    }else if(dicingerPro_TD.df['dicingerPro_TD.linear', dfind[2]] == 1){
      Proba.df['dicingerPro_TD.linear', "up_flag"] <- 1
      Proba.df['dicingerPro_TD.linear', "down_flag"] <- 0
    }
    Proba.df['dicingerPro_TD.linear', 'acc.'] <- dicingerPro_TD.df['dicingerPro_TD.linear', dfind[1]]
  }
  # Read dicingerPro_TD.CNN module
  if(length(dfind)==2){
    if(dicingerPro_TD.df['dicingerPro_TD.CNN', dfind[2]] == "[0]"){
      Proba.df['dicingerPro_TD.CNN', "up_flag"] <- 0
      Proba.df['dicingerPro_TD.CNN', "down_flag"] <- 1
    }else if(dicingerPro_TD.df['dicingerPro_TD.CNN', dfind[2]] == "[1]"){
      Proba.df['dicingerPro_TD.CNN', "up_flag"] <- 1
      Proba.df['dicingerPro_TD.CNN', "down_flag"] <- 0
    }
    Proba.df['dicingerPro_TD.CNN', 'acc.'] <- dicingerPro_TD.df['dicingerPro_TD.CNN', dfind[1]]
  }
  # Read dicingerPro_TD.RNN module
  if(length(dfind)==2){
    if(dicingerPro_TD.df['dicingerPro_TD.RNN', dfind[2]] == 0){
      Proba.df['dicingerPro_TD.RNN', "up_flag"] <- 0
      Proba.df['dicingerPro_TD.RNN', "down_flag"] <- 1
    }else if(dicingerPro_TD.df['dicingerPro_TD.RNN', dfind[2]] == 1){
      Proba.df['dicingerPro_TD.RNN', "up_flag"] <- 1
      Proba.df['dicingerPro_TD.RNN', "down_flag"] <- 0
    }
    Proba.df['dicingerPro_TD.RNN', 'acc.'] <- dicingerPro_TD.df['dicingerPro_TD.RNN', dfind[1]]
  }

  dfind <- grep(pattern, colnames(dicingerPro_S.df))
  # Read dicingerPro_S.linear module
  if(length(dfind)==2){
    if(dicingerPro_S.df['dicingerPro_S.linear', dfind[2]] == 0){
      Proba.df['dicingerPro_S.linear', "up_flag"] <- 0
      Proba.df['dicingerPro_S.linear', "down_flag"] <- 1
    }else if(dicingerPro_S.df['dicingerPro_S.linear', dfind[2]] == 1){
      Proba.df['dicingerPro_S.linear', "up_flag"] <- 1
      Proba.df['dicingerPro_S.linear', "down_flag"] <- 0
    }
    Proba.df['dicingerPro_S.linear', 'acc.'] <- dicingerPro_S.df['dicingerPro_S.linear', dfind[1]]
  }
  # Read dicingerPro_S.CNN module
  if(length(dfind)==2){
    if(dicingerPro_S.df['dicingerPro_S.CNN', dfind[2]] == "[0]"){
      Proba.df['dicingerPro_S.CNN', "up_flag"] <- 0
      Proba.df['dicingerPro_S.CNN', "down_flag"] <- 1
    }else if(dicingerPro_S.df['dicingerPro_S.CNN', dfind[2]] == "[1]"){
      Proba.df['dicingerPro_S.CNN', "up_flag"] <- 1
      Proba.df['dicingerPro_S.CNN', "down_flag"] <- 0
    }
    Proba.df['dicingerPro_S.CNN', 'acc.'] <- dicingerPro_S.df['dicingerPro_S.CNN', dfind[1]]
  }
  # Read dicingerPro_S.RNN module
  if(length(dfind)==2){
    if(dicingerPro_S.df['dicingerPro_S.RNN', dfind[2]] == 0){
      Proba.df['dicingerPro_S.RNN', "up_flag"] <- 0
      Proba.df['dicingerPro_S.RNN', "down_flag"] <- 1
    }else if(dicingerPro_S.df['dicingerPro_S.RNN', dfind[2]] == 1){
      Proba.df['dicingerPro_S.RNN', "up_flag"] <- 1
      Proba.df['dicingerPro_S.RNN', "down_flag"] <- 0
    }
    Proba.df['dicingerPro_S.RNN', 'acc.'] <- dicingerPro_S.df['dicingerPro_S.RNN', dfind[1]]
  }
  
  # # Majority Voting, the ensemble approach.-----------------------------------
  error_up <- Proba.df[which(Proba.df$up_flag==1), ]
  error_down <- Proba.df[which(Proba.df$down_flag==1), ]
  up_flags <- count(Proba.df, up_flag)
  down_flags <- count(Proba.df, down_flag)
  if(!(is.na(up_flags[1, 1]))){
      rownames(up_flags) <- up_flags[, 'up_flag']
      rownames(down_flags) <- down_flags[, 'down_flag']
      if(!(is.na(up_flags['1',1]))){
        k_up_flags <- up_flags['1', ]
      }else if(is.na(up_flags['1',1])){
        k_up_flags <- data.frame(up_flag=0, n=0)
        rownames(k_up_flags) <- 1
      }
      
      k_down_flags <- down_flags['1', ]
      if(k_up_flags['1', 'n'] > 4){
        ensemble_error <- 0
        error <- mean(1 - unlist(error_up['acc.']))
        for(k in 4:k_up_flags['1', 'n']){
          ensemble_error <- ensemble_error + length(combn(9, k, simplify = FALSE)) * error ** k * (1-error) ** (9 - k)
        }
        ensemble_accuracy <- 1-ensemble_error
        returnSuggestion <- paste0(indexWanted, " is predicted to GO UP as\n", 
                                   k_up_flags['1', 'n'], " out of 9 modules indicated that \nwith an accuracy of ", 
                                   round(ensemble_accuracy*100), "%.")
      }else if(k_down_flags['1', 'n'] > 4){
        ensemble_error <- 0
        error <- mean(1 - unlist(error_down['acc.']))
        for(k in 4:k_down_flags['1', 'n']){
          ensemble_error <- ensemble_error + length(combn(9, k, simplify = FALSE)) * error ** k * (1-error) ** (9 - k)
        }
        ensemble_accuracy <- 1-ensemble_error
        returnSuggestion <- paste0(indexWanted, " is predicted to GO DOWN as\n", 
                                   k_down_flags['1', 'n'], " out of 9 modules indicated that \nwith an accuracy of ", 
                                   round(ensemble_accuracy*100), "%.")
      }else{
        returnSuggestion <- paste0(indexWanted, " is predicted to STAY FLAT.")
      }
  }
  return(list(Proba.df, returnSuggestion))
}

# # Generate all the probabilities.---------------------------------------------
# Obtain the indexes of all the targets.
indexes_csv <- read_csv(file.path("~/PRO80", "DailyTDs/ref_TD.csv")) 
indexes_list <- unlist(indexes_csv[1, ])
```

## PROBABILITY TABLE {.tabset}

### COPPER

```{r}
indexWanted = "CU0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### SOYOIL

```{r}
indexWanted = "Y0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### PALMOIL

```{r}
indexWanted = "P0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### RUBBER

```{r}
indexWanted = "RU0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### SILVER

```{r}
indexWanted = "AG0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### BITUMAN

```{r}
indexWanted = "BU0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### ZNIC

```{r}
indexWanted = "ZN0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### PTA

```{r}
indexWanted = "TA0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### ALUMINUM

```{r}
indexWanted = "AL0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### L

```{r}
indexWanted = "L0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### PVC

```{r}
indexWanted = "V0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### CF

```{r}
indexWanted = "CF0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### PP

```{r}
indexWanted = "PP0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### RB

```{r}
indexWanted = "RB0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### HC

```{r}
indexWanted = "HC0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### IRONORE

```{r}
indexWanted = "I0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### MA

```{r}
indexWanted = "MA0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### FG

```{r}
indexWanted = "FG0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### AU

```{r}
indexWanted = "AU0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### FU

```{r}
indexWanted = "FU0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### SR

```{r}
indexWanted = "SR0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### M

```{r}
indexWanted = "M0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

# UP AND DOWN SOCKETS

## UP SOCKETS {.tabset}

### UP_SOCK(1)

```{r}
indexWanted = "RB0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### UP_SOCK(2)

```{r}
indexWanted = "HC0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### UP_SOCK(3)

```{r}
indexWanted = "TA0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### UP_SOCK(4)

```{r}
indexWanted = "FU0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### UP_SOCK(5)

```{r}
indexWanted = "MA0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

## DOWN SOCKETS {.tabset}

### DOWN_SOCK(1)

```{r}
indexWanted = "ZN0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### DOWN_SOCK(2)

```{r}
indexWanted = "V0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### DOWN_SOCK(3)

```{r}
indexWanted = "SR0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### DOWN_SOCK(4)

```{r}
indexWanted = "FG0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```

### DOWN_SOCK(5)

```{r}
indexWanted = "AL0"
probaTable <- create_Proba(indexWanted)
cat(probaTable[[2]])
knitr::kable(probaTable[[1]])
```